Growth Resilience

### 2017-09-06 analysis/analysis_resilience_bai.Rmd
update resilience bai

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8,warning=FALSE, message=FALSE)
```

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("dplR")
library("stringr")
library("knitr")
library('gtable')
library('grid')
library('gridExtra')
library('pander')
library('broom')
library('effects')
library('devtools')
# devtools::install_github("ajpelu/auxiliar")
library('car')
library('auxiliar')
library('WRS2')
library('MASS')
library('rcompanion')
```

# Resilience

@@

for (i in obj){ 
  x <- get(i)
  xres <- x$resilience
  out <- xres %>% 
    mutate(ws = paste0('ws_', as.character(str_extract(i, "([0-9])"))),
           site = str_replace(i, "res_[0-9]_", '')) %>%
    select(-disturb_year, -tree)

@@

cor2 <- correla[["ws_2"]] %>% select(-ws) %>% mutate(ind = row_number())
cor3 <- correla[["ws_3"]] %>% select(-ws) %>% mutate(ind = row_number())
cor4 <- correla[["ws_4"]] %>% select(-ws) %>% mutate(ind = row_number())

@@

g %>% mutate(disturb = recode(disturb, 
                              dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  ggplot(aes(y=mean_period/100, x=disturb)) + 
  geom_boxplot() + 
  facet_grid(site~disturb_year, scales='free_y') + 
  theme_bw()
```

## Mean + se 
```{r}
g %>% 
  mutate(disturb = recode(disturb, dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  group_by(disturb, disturb_year, site) %>% 
  summarise(mean = mean(mean_period),
            sd = sd(mean_period),
            se = sd/sqrt(length(mean_period))) %>%
  ggplot(aes(y=mean/100, x=disturb)) + 
  geom_errorbar(aes(ymin=mean/100 - se/100, 
                    ymax=mean/100 + se/100),
                width = 0.2) +
  geom_point(size=2, shape=21, fill='white') + 
  facet_grid(site~disturb_year, scales='free_y') + 
  theme_bw() + ylab('BAI (cm2/year)') + 
  theme(panel.grid = element_blank())
```

```{r}
pgrowht <- g %>% 
  mutate(disturb = recode(disturb, dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  group_by(disturb, disturb_year, site) %>% 
  summarise(mean = mean(mean_period),
            sd = sd(mean_period),
            se = sd/sqrt(length(mean_period))) %>%
  ggplot(aes(y=mean/100, x=disturb, colour=site)) + 
  geom_errorbar(aes(ymin=mean/100 - se/100, 
                    ymax=mean/100 + se/100),
                width = 0.15) +
  geom_point(size=3, aes(shape=site), fill='white') + 
  geom_line(aes(group=site))+
  facet_wrap(~disturb_year, scales='free_y') + 
  theme_bw() + ylab('BAI (cm2/year)') + 
  theme(panel.grid = element_blank())

@@

```{r}
g %>% 
  mutate(disturb = recode(disturb, dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  dplyr::group_by(site, disturb_year, disturb) %>% 
  dplyr::summarise(mean = mean(mean_period/100), 
                   sd = sd(mean_period/100),
                   se = sd/sqrt(length(mean_period/100))) %>% as.data.frame() %>% pander() 
```

@@

```{r}
# Only 2005 and 2012
re <- re %>% filter(disturb_year != 1995) %>% as.data.frame()
vars <- c('disturb_year','site')
```

@@

  df <- re
  alpha = 0.95
  nboot = 3000
  treshold = 0.01

@@

@@

  ## factor B
  phb <- pairwiseRobustTest(formula_B, data = df, est = "mom", 
                            nboot = nboot, method="bonferroni")
  ## interaction effect (AB)
  phab <- pairwiseRobustTest(formula_AB, data = df, est = "mom", 
                            nboot = nboot, method="bonferroni")
  ## letters
  letters_pha <- cldList(comparison = pha$Comparison,
        p.value    = pha$p.adjust,
        threshold  = treshold)
  letters_phb <- cldList(comparison = phb$Comparison,
        p.value    = phb$p.adjust,
        threshold  = treshold)

  letters_phab <- cldList(comparison = phab$Comparison,
        p.value    = phab$p.adjust,
        threshold  = treshold)

@@

  out <- list()  
  out$mest <- mest # Huber M-estimators and Confidence Intervals
  out$mest_a <- mest_a
  out$mest_b <- mest_b
  out$ra <- out_ra # Output for Two-way robust analysis (M-estimators)
  out$letters_pha <- if(exists(letters_pha), letters_pha,  # Letters comparison posthoc
  out$letters_phb <- letters_pha # Letters comparison posthoc
  out$letters_phab <- letters_pha # Letters comparison posthoc
  out$ph <- ph # posthoc comparison usinng pairwiseRobustTest

@@

  return(out)
}
```

```{r}
factores = c('disturb_year', 'site', 'disturb_year:site')

@@

```{r}
rars <- robustANOVA(df=re, resp_var='rs', factores=factores,
              alpha = 0.95, nboot = 3000, treshold = 0.01)
```

```{r}
rarc <- robustANOVA(df=evires, resp_var='rc', factores=factores,
              alpha = 0.95, nboot = 3000, treshold = 0.01)
```

```{r}
rart <- robustANOVA(df=evires, resp_var='rt', factores=factores,
              alpha = 0.95, nboot = 3000, treshold = 0.01)
```

```{r}
rarrs <- robustANOVA(df=evires, resp_var='rrs', factores=factores,
              alpha = 0.95, nboot = 3000, treshold = 0.01)
```

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8,warning=FALSE, error=TRUE, message=FALSE)
```

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("dplR")
library("stringr")
library("knitr")
library('gtable')
library('grid')
library('gridExtra')
library('pander')
library('broom')
library('effects')
library('devtools')
# devtools::install_github("ajpelu/auxiliar")
library('car')
library('auxiliar')
library('WRS2')
library('MASS')
library('rcompanion')
```
# Resilience

@@

for (i in obj){ 
  x <- get(i)
  xres <- x$resilience
  out <- xres %>% 
    mutate(ws = paste0('ws_', as.character(str_extract(i, "([0-9])"))),
           site = str_replace(i, "res_[0-9]_", '')) %>%
    dplyr::select(-disturb_year, -tree)

@@

cor2 <- correla[["ws_2"]] %>% dplyr::select(-ws) %>% mutate(ind = row_number())
cor3 <- correla[["ws_3"]] %>% dplyr::select(-ws) %>% mutate(ind = row_number())
cor4 <- correla[["ws_4"]] %>% dplyr::select(-ws) %>% mutate(ind = row_number())

@@

g %>% mutate(disturb = dplyr::recode(disturb, 
                              dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  ggplot(aes(y=mean_period/100, x=disturb)) + 
  geom_boxplot() + 
  facet_grid(site~disturb_year, scales='free_y') + 
  theme_bw()
```

## Mean + se 
```{r}
g %>% 
  mutate(disturb = dplyr::recode(disturb, dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  group_by(disturb, disturb_year, site) %>% 
  summarise(mean = mean(mean_period),
            sd = sd(mean_period),
            se = sd/sqrt(length(mean_period))) %>%
  ggplot(aes(y=mean/100, x=disturb)) + 
  geom_errorbar(aes(ymin=mean/100 - se/100, 
                    ymax=mean/100 + se/100),
                width = 0.2) +
  geom_point(size=2, shape=21, fill='white') + 
  facet_grid(site~disturb_year, scales='free_y') + 
  theme_bw() + ylab('BAI (cm2/year)') + 
  theme(panel.grid = element_blank())
```

```{r}
pgrowht <- g %>% 
  mutate(disturb = dplyr::recode(disturb, dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  group_by(disturb, disturb_year, site) %>% 
  summarise(mean = mean(mean_period),
            sd = sd(mean_period),
            se = sd/sqrt(length(mean_period))) %>%
  ggplot(aes(y=mean/100, x=disturb, colour=site)) + 
  geom_errorbar(aes(ymin=mean/100 - se/100, 
                    ymax=mean/100 + se/100),
                width = 0.15) +
  geom_point(size=3, aes(shape=site), fill='white') + 
  geom_line(aes(group=site))+
  facet_wrap(~disturb_year, scales='free_y') + 
  theme_bw() + ylab('BAI (cm2/year)') + 
  theme(panel.grid = element_blank())

@@

```{r}
g %>% 
  mutate(disturb = dplyr::recode(disturb, dr = '1_dr', pre = '0_pre', post = '2_post')) %>%
  dplyr::group_by(site, disturb_year, disturb) %>% 
  dplyr::summarise(mean = mean(mean_period/100), 
                   sd = sd(mean_period/100),
                   se = sd/sqrt(length(mean_period/100))) %>% as.data.frame() %>% pander() 
```

@@

```{r}
# Only 2005 and 2012
re <- re %>% filter(disturb_year != 1995) %>% as.data.frame()
vars <- c('disturb_year','site')
re$disturb_year <- factor(re$disturb_year)
```

@@

@@

  pbad2way(rs ~ disturb_year + site + disturb_year:site, data = df, 
           est = "mom", nboot = nboot)

@@

  ## factor B
  phb <- pairwiseRobustTest(formula_B, data = df, est = "mom", 
                            nboot = nboot, method="bonferroni")
  ## interaction effect (AB)
  phab <- pairwiseRobustTest(formula_AB, data = df, est = "mom", 
                            nboot = nboot, method="bonferroni")

@@

  out <- list()  
  out$mest <- mest # Huber M-estimators and Confidence Intervals
  out$mest_a <- mest_a
  out$mest_b <- mest_b
  out$ra <- out_ra # Output for Two-way robust analysis (M-estimators)
  out$ph <- ph # posthoc comparison usinng pairwiseRobustTest 
  out$pha <- pha
  out$phb <- phb
  out$phab <- phab

@@

  # if (exists('letters_phb')) {
  # letters_phb <- letters_phb} else {
  # myerror <- evaluate('cldList(comparison = phb$Comparison, 
  #                     p.value = phb$p.adjust, threshold  = treshold)')
  # letters_phb <- as.character(myerror[[2]]$message)}
  # 
  # if (exists('letters_pha')) {
  # letters_pha <- letters_pha} else {
  # myerror <- evaluate('cldList(comparison = pha$Comparison, 
  #                     p.value = pha$p.adjust, threshold  = treshold)')
  # letters_pha <- as.character(myerror[[2]]$message)}
  # 
  # if (exists('letters_phab')) {
  # letters_phab <- letters_phab} else {
  # myerror <- evaluate('cldList(comparison = phab$Comparison, 
  #                     p.value = phab$p.adjust, threshold  = treshold)')
  # letters_phab <- as.character(myerror[[2]]$message)}

@@

```{r}
factores = c('disturb_year', 'site', 'disturb_year:site')
```

## Resilience 
```{r}
rars <- robustANOVA(df=re, resp_var='rs', factores=factores,
              alpha = 0.95, nboot = 3000, treshold = 0.01)
```

#### Rs Letters 
```{r}
x <-rars

cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01)
cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01)
cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01)
```

## Recovery 
```{r}
rarc <- robustANOVA(df=re, resp_var='rc', factores=factores,
              alpha = 0.95, nboot = 3000, treshold = 0.01)
```

#### Rc Letters 
```{r}
x <-rarc

cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01)
cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01)
cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01)
```

## Resistance 
```{r}
rart <- robustANOVA(df=re, resp_var='rt', factores=factores,
              alpha = 0.95, nboot = 3000, treshold = 0.01)
```

#### Rt Letters 
```{r}
x <-rart

cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01)
cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01)
cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01)
```

## Relative Resilience
```{r}
rarrs <- robustANOVA(df=re, resp_var='rrs', factores=factores,
              alpha = 0.95, nboot = 3000, treshold = 0.01)
```

#### Rt Letters 
```{r}
x <-rarrs

cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01)
cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01)
cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01)
```

### Estimadores de huber 
```{r} 
rars$mest$var <- 'rs'
rarc$mest$var <- 'rc'
rart$mest$var <- 'rt'
rarrs$mest$var <- 'rrs'

mhuber <- rbind(rarc$mest, rart$mest, rars$mest, rarrs$mest)
mhuber %>% pander()
```

```{r}
rars$mest_a$var <- 'rs'
rarc$mest_a$var <- 'rc'
rart$mest_a$var <- 'rt'
rarrs$mest_a$var <- 'rrs'

mhuber_a <- rbind(rarc$mest_a, rart$mest_a, rars$mest_a, rarrs$mest_a)
mhuber_a %>% pander()
```

```{r}
rars$mest_b$var <- 'rs'
rarc$mest_b$var <- 'rc'
rart$mest_b$var <- 'rt'
rarrs$mest_b$var <- 'rrs'

mhuber_b <- rbind(rarc$mest_b, rart$mest_b, rars$mest_b, rarrs$mest_b)
mhuber_b %>% pander()
```

### Pairwise comparison
```{r}

rars$ph$var <- 'rs'
rarc$ph$var <- 'rc'
rart$ph$var <- 'rt'
rarrs$ph$var <- 'rrs'

pairwise <- rbind(rarc$ph, rart$ph, rars$ph, rarrs$ph) 
pairwise %>% pander()
```

## Interaction plot 
### Response ~ (x=Drought)

```{r}
mhuber<- mhuber %>% 
  mutate(var_sorted = case_when(var == "rc" ~ "1_rc",
                                var == "rt" ~ "0_rt",
                                var == "rs" ~ "2_rs",
                                var == "rrs" ~ "3_rrs"))

pd <- position_dodge(.2)

robust_plot_evi_drought <- ggplot(mhuber, aes(x=disturb_year, y=M.Huber, color = site, group=site, fill=site)) + 
  geom_errorbar(aes(ymin=lower.ci, ymax=upper.ci), 
                width=.1, size=0.7, position=pd) + 
  geom_line(aes(group=site,color=site, linetype=site), position=pd) + 
  geom_point(shape=21, size=3.5, position=pd) +
  facet_wrap(~var_sorted, nrow = 2, scales = 'free_y',
             labeller=as_labeller(c('0_rt' = 'Resistance', 
                                 '1_rc' = 'Recovery',
                                 '2_rs' = 'Resilience',
                                 '3_rrs' = 'Relative Resilience'))) +
  scale_color_manual(values=c('black','blue','red')) + 
  scale_fill_manual(values=c('black','blue','red')) + theme_bw() +
  scale_linetype_manual(values=c("solid", "dashed", 'dashed')) +
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'),
        legend.position="bottom") +
  ylab('') + xlab('Drought event')

robust_plot_evi_drought

pdf(paste0(di, 'out/fig/resilience/robust_plot_evi_drought.pdf'), width=9, height = 9)
robust_plot_evi_drought 
dev.off()
```

### Response ~ (x=site)
```{r}
pd <- position_dodge(.2)

robust_plot_evi_site <- ggplot(mhuber, aes(x=site, y=M.Huber, color = disturb_year, group=disturb_year, fill=disturb_year)) + 
  geom_errorbar(aes(ymin=lower.ci, ymax=upper.ci), 
                width=.1, size=0.7, position=pd) + 
  geom_line(aes(group=disturb_year,color=disturb_year, linetype=disturb_year), position=pd) + 
  geom_point(shape=21, size=3.5, position=pd) +
  facet_wrap(~var_sorted, nrow = 2, scales = 'free_y',
             labeller=as_labeller(c('0_rt' = 'Resistance', 
                                 '1_rc' = 'Recovery',
                                 '2_rs' = 'Resilience',
                                 '3_rrs' = 'Relative Resilience'))) +
  scale_color_manual(values=c('black','blue')) + 
  scale_fill_manual(values=c('black','blue')) + theme_bw() +
  scale_linetype_manual(values=c("solid", "dashed")) +
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'),
        legend.position="bottom") +
  ylab('') + xlab('Drought event')

robust_plot_evi_site

pdf(paste0(di, 'out/fig/resilience/robust_plot_evi_site.pdf'), width=9, height = 9)
robust_plot_evi_site 
dev.off()
```

```{r}
# Export data 
write.csv(mhuber, file=paste0(di, '/out/anovas_resilience/robust_mhuber.csv'), row.names = F)
write.csv(mhuber_a, file=paste0(di, '/out/anovas_resilience/robust_mhuber_a.csv'), row.names = F)
write.csv(mhuber_b, file=paste0(di, '/out/anovas_resilience/robust_mhuber_b.csv'), row.names = F)

write.csv(pairwise, file=paste0(di, '/out/anovas_resilience/robust_pairwise.csv'), row.names = F)
```
